---
title: "Ass 4"
author: "Nathanael Reese"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
    theme: darkly
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Completed 10/10

### Task 1

(a)
```{r}
library(LaF)
# Function that samples the file
sample1 <- function(file, n) {
  lf <- laf_open(detect_dm_csv(file, sep = ",", header = TRUE, factor_fraction = -1))
  return(read_lines(lf, sample(1:nrow(lf), n)))
}
```

**sample**

```{r}
sample <- sample1("NZBIRDS.csv", 35)
```

#### (b)

```{r}
mp <- c(-1,1)
mean(sample$Body.Mass) + mp*qt(1-.05,34)*sd(sample$Body.Mass)/sqrt(35)
```

#### (c)

The mean of the sampled birds' body masses will fall in the itnerval with 95% confidence

###(d)

The interval is 95% confidence, which is why it is very likely to contain mu

#### (e)

```{r} mean(sample$Egg.Length) + mp*qt(1-.05,34)*sd(sample$Egg.Length)/sqrt(35)```
The mean of the sampled birds' Egg Length will fall in the itnerval with 95% confidence

The interval is 95% confidence, which is why it is very likely to contain mu

#### (f)
```{r}
n1 = 38 # total extinct
n2 = 78 # total not extinct

p1hat = 21 / n1  
q1hat = 1 - p1hat
p2hat = 7 / n2
q2hat = 1 - p2hat

mp = c(-1,1)
ci <- (p1hat - p2hat) + mp * qnorm(1-.05/2,0,1)*sqrt((p1hat*q1hat/n1) + (p2hat*q2hat/n2))
ci
```


### Task 2

```{r}

```

### Task 3


```{r}

```

### Task 4

```{r}

```

### Task 5



```{r}

```


### Task 6

```{r}
```


### Task 7

```{r}

```

### Task 8

```{r}
```

### Task 9

```{r}
```

### Task 10

```{r}
```
